---
title: "Impact Intelligence Assessment"
output: github_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE,
                      message = FALSE,
                      warning = FALSE)


```


### Load R packages to use

```{r}
library(tidyverse)
library(data.table)
library(readxl)
library(xlsx)
library(knitr)
```

### Read data into R

```{r}
topic_an  <- read_excel("data/Impact Intelligence - Project Contractor Sample.xlsx", sheet = 4)
topic_metrics  <- read_excel("data/Impact Intelligence - Project Contractor Sample.xlsx", sheet = 3)

```

### Save the names of the two sheets

```{r}
# convert to DT
setDT(topic_an)

nms_topic <- names(topic_an)
nms_topic_metrics <- names(topic_metrics)

```

### Function to clean names
- ie it removes white space and other characters to make it easier to use a programming language like R or python etc.

```{r}
nms_clean <- function(data_set){
  nms_old <- names(data_set)
  nms_new <- nms_old %>% tolower() 
  nms_new <- gsub("\\s", "_", nms_new)
  nms_new <- gsub("\\.$", "", nms_new)
  nms_new <- gsub("\\(|\\)|%", "", nms_new)
  nms_new <- gsub("/", "", nms_new)
  
  setDT(data_set)
  setnames(data_set, nms_old, nms_new)
  data_set
}
```

### Clean names

```{r}
topic_an <- nms_clean(topic_an)
topic_metrics <- nms_clean(topic_metrics)
nms_topic_metrics_clean <- names(topic_metrics)

```

### Some other minor cleaning 


```{r}
## filter out topics where they are irrelevant
topic_an <- topic_an[!grepl("irrelevant", topic_name)]

## extract topic id so that it's easier to merge
topic_an[, topic_id := str_extract(topic_label, "^\\d{1,3}[^\\.]")]

## delete topic label so that you only have one topic label in the data

topic_an[, topic_label := NULL]

#merge the two data sets
topic_an_ans <- merge(topic_an, topic_metrics, by = "topic_id")

## calculate Share of Voice on all Topics
topic_an_ans[, share_voice := round(segment_count/sum(topic_metrics$segment_count), 4)]
## order with share voice and select top 5 descending
setorder(topic_an_ans, -share_voice)
## select top 5
topic_an_ans <- topic_an_ans[1:5,]
## Rename to the original names

head(topic_an_ans) %>%
  kable()
```

### Rename back columns to original names

```{r}
nms_final_dt <- names(topic_an_ans)

setnames(topic_an_ans,
         nms_topic_metrics_clean, 
         nms_topic_metrics, skip_absent = T)

nms_to_rnm <- c("topic_name", "share_voice",
                "Overrepresented Keywords")

nms_to_rnm_to <- c("Topic Name", 
                   "Share of Voice on all Topics",
                   "Keywords")

setnames(topic_an_ans,
         nms_to_rnm, 
         nms_to_rnm_to, skip_absent = F)

```


### Select required columns 

```{r}
nms_required <- c("Topic Name", "Share of Voice on all Topics",
                  "Average Sentiment", "Average Engagement", "Keywords")

output_df <- topic_an_ans[, ..nms_required]

```

### Delete output sheet
- it will enable in writing to it
 
```{r}
wb_path <- "data/Impact Intelligence - Project Contractor Sample.xlsx"
wb <- loadWorkbook(wb_path)
removeSheet(wb, sheetName = "Output")
saveWorkbook(wb, wb_path)
```

### Append the sheet to your excel workbook

```{r}
## Then append the sheet to your excel workbook
write.xlsx(as.data.frame(output_df), 
           file = "data/Impact Intelligence - Project Contractor Sample.xlsx", 
           sheetName="Output",
           append=TRUE,
           row.names = F)

```

